Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-24 ms.tex
more about dust emission model

%the below statements seem like they might best be moved to a generic
%opening of the next section, stating our philosophy of breaking sky
%into pixels, each with 5 SED measurements, and that with this small
%number of constraints per pixel, it makes sense to have a baseline
% fit at full resolution that has only two free parameters
At each sky location, our baseline fit at the full $6.1'$ resolution 
incorporates only five independent intensity measurements (\verb|i100| along 
with the four highest-frequency \PLANCK~bands). FDS99 found typical values for 
$T_2$ and

>>>>

%the below statements seem like they might best be moved to a generic
%opening of the next section, stating our philosophy of breaking sky
%into pixels, each with 5 SED measurements, and that with this small
%number of constraints per pixel, it makes sense to have a baseline
% fit at full resolution that has only two free parameters
FDS99 found $T_2 \approx 16.2$K, $T_1 \approx 9.4$K to be typical at 
high-latitude. In the present formulation, there are only two free parameters 
to describe an observed SED: the hot dust temperature $T_2$ and the 
normalization of $M_{\nu}$. In principle, we could allow additional parameters,
 such as $f_1$ and the ratio $q_1/q_2$, to vary. However the number of free 
parameters in our baseline fit at the full $6.1'$ resolution is limited by the 
fact that, for each sky location, the observed SED contains only five 
independent intensity measurements (\verb|i100| along with the four 
highest-frequency \PLANCK~bands).
